Variability of Planetary Mass Companion 2M1207 B

### 2015-08-25 summary/letter/letter_vAB.tex
including more pixels

We present here, for the first time, time-resolved high-precision
photometric measurements of a planetary-mass companion, 2MASS1207b, to
a brown dwarf primary. Using HST/WFC3 and point spread function %in
combination with two spacecraft roll angles we detect photometric
modulations in the light curve. The amplitude is 0.9\% in the F160W
and 1.5\% in the F125W filters; we find a consistent period and
similar phase in both bands. Joint fit to the lightcurve in both bands
suggest a period of 10.0$\pm$0.9h. The relative amplitudes in the two
filters are very similar to that found in a recent study of a field
(high-gravity) L-dwarf, suggesting that the cloud structures that
introduce the photometric modulations are similar in high- and
low-gravity objects. Importantly, our study also measures, for the
first time, the rotational period for directly imaged planetary-mass
companion.
\end{abstract}

@@

First, we fitted sine waves independently to the two filters to verify
the similarity of the signal in the two bands (Figure \ref{fig:2}). Inconsistent periods or
light curve shapes would argue against a genuine signal.  We found
that the periods of the best fit sine waves are very similar,
$10.45^{+1.2}_{-1.3}$h for F125W and $9.0^{+1.1}_{-1.2}$h for
F160W. These periods are consistent within the
uncertainty. Furthermore, these periods are not close to any
timescales over which HST or WFC3 are known to changes.

@@

The distributions for the periods demonstrate long tail shaped towards
long period, with core region roughly Gaussian. With probability range
of 64\%(1-$\sigma$ Gaussian), we estimated the 1-$\sigma$ standard
deviations for the periods of F125W and F160W to be 1.2 h and 1.5 h. The period for best
fitted sine wave of F125W light curve is longer than that of F160W for
1.4 h that is around 1-$\sigma$ standard deviation. We also
performed a joint MC fit with the two light curves with the assumption
that the periods of the variation of the two bands are the same. We
derived a period of $10.0\pm0.9$ h.

>>>>

We present here, for the first time, time-resolved high-precision
photometric measurements of a planetary-mass companion, 2MASS1207b, to
a brown dwarf primary. Using HST/WFC3 and point spread function %in
combination with two spacecraft roll angles we detect photometric
modulations in the light curve. The amplitude is 0.9\% in the F160W
and 1.5\% in the F125W filters; we find a consistent period and
similar phase in both bands. Joint fit to the lightcurve in both bands
suggest a period of $10.2^{+0.9}_{-0.8}$ h. The relative amplitudes in the two
filters are very similar to that found in a recent study of a field
(high-gravity) L-dwarf, suggesting that the cloud structures that
introduce the photometric modulations are similar in high- and
low-gravity objects. Importantly, our study also measures, for the
first time, the rotational period for directly imaged planetary-mass
companion.
\end{abstract}

@@

First, we fitted sine waves independently to the two filters to verify
the similarity of the signal in the two bands (Figure \ref{fig:2}). Inconsistent periods or
light curve shapes would argue against a genuine signal.  We found
that the periods of the best fit sine waves are similar,
$10.5^{+1.2}_{-1.3}$h for F125W and $9.1^{+1.1}_{-1.0}$h for
F160W. These periods are roughly consistent within the
uncertainty. Furthermore, these periods are not close to any
timescales over which HST or WFC3 are known to changes.

@@

The distributions for the periods demonstrate long tail shaped towards
long period, with core region roughly Gaussian. With probability range
of 64\%(1-$\sigma$ Gaussian), we estimated the 1-$\sigma$ range for
the periods of F125W and F160W to be  $10.5_{-1.2}^{+1.3}$ and
$9.1_{-1.0}^{+1.1}$ h, respectively. The period for best
fitted sine wave of F125W light curve is longer than that of F160W for
1.5 h that is slight larger 1-$\sigma$ standard deviation. We also
performed a joint MC fit with the two light curves with the assumption
that the periods of the variation of the two bands are the same. We
derived a period of $10.2^{+0.9}_{-0.8}$ h.
